### 2012-11-17 inst/examples/mult_uncertainty_test.Rmd
Comparison of each type of uncertainty (e.g. Figure 3)

Tmax = 25
sigmas =c (sigma_g=.3, sigma_m=0.3, sigma_i=0.3)

@@

    # integrate over uncertainty in I and X 
    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- sum(sapply(1:n_x, function(x)
          f(x_grid[x],h_grid,p) %*% I[q,] *  M[y,x])) # Implementation & Measurement error
        if(mu==0)
          out[1] <- 1 ## Wow, really? should we be applying noise to the f*I*M product or the f?  
        else 
          out <- dlnorm(x_grid/mu, 0, sigma_g)
        out/sum(out)
      }))
    })

@@

```{r mult_uncertainty}
new <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0, sigma_i=0), pdfn=pdfn)  
m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0.1, sigma_i=0), pdfn=pdfn)
i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=sigma_g, sigma_m=0, sigma_i=0.1), pdfn=pdfn)
```

@@

```{r}
rbind(opt$D[,1], new$D[,1], m$D[,1], i$D[,1])
```

>>>>

@@

    # integrate over uncertainty in I and X 
    F <- lapply(1:n_h, function(q){  
      t(sapply(1:n_x, function(y){
        out <- numeric(n_x)
        mu <- sum(sapply(1:n_x, function(x)
          f(x_grid[x],h_grid,p) %*% I[q,] *  M[y,x])) # Implementation & Measurement error
        if(mu==0)
          out[1] <- 1   
        else 
          out <- dlnorm(x_grid/mu, 0, sigma_g)
        out/sum(out)
      }))
    })

@@

```{r mult_uncertainty}
out <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0.3, sigma_i=0.3), pdfn=pdfn)  
```

```{r noisetypes}
new <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0, sigma_i=0), pdfn=pdfn)  
m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0.3, sigma_i=0), pdfn=pdfn)  
i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, OptTime, sigmas = c(sigma_g=0.3, sigma_m=0, sigma_i=0.3), pdfn=pdfn)  
```

@@
